% Adapted from template by Rajib Das Bhagat (rajibdasbhagat@gmail.com) https://www.overleaf.com/latex/templates/job-application-cover-letter/jgbntsgkcvvz
%
\documentclass[11pt,a4paper,roman]{moderncv}      
\usepackage[english]{babel}

\moderncvstyle{classic}                            
\moderncvcolor{black}                            

% character encoding
\usepackage[utf8]{inputenc}                     

% adjust the page margins
\usepackage[scale=0.80]{geometry}

% custom commands - John
\newcommand{\companyName}{Twitch}
\newcommand{\companyDivision}{Twitch Music}
\newcommand{\positionName}{Software Engineer}

% personal data
\name{John Jones}{}
\title{\companyName{} Cover Letter}
\email{johnj.gw@gmail.com}
\phone[mobile]{+1 785-201-1063}               
\address{Overland Park, KS 66210}


\begin{document}

\recipient{To}{Twitch Interactive, Inc. \\
               San Francisco, CA}
\date{\today}
\opening{\textbf{Application for \positionName{} - \companyDivision.}}
\closing{Sincerely, \vspace{-1em}}



\makelettertitle



Dear Hiring Manager,
\\
%references such as what and how you got this information
\vspace{1em}
I'm excited to be applying for the Software Engineer position at \companyName. As someone who is highly focused and attentive to detail, 
I thrive on building quality systems that surpass end users' expectations. 
I'm thrilled at the opportunity to show off my technical expertise and leadership skills as part of \companyName's expert team.
%narrate why you want to apply
\vspace{1em}
Being a fresher officially, I can compile subjects such as C-Programming, Data Structures, Algorithms, Operating System, Digital Electronics, Deep Learning and Neural Networks, Web Applications and Software Engineering. I take friendly and logical approach towards solving a problem from the very basis to the optimized version.  \\
\vspace{1em}

%add some experiences 
I have some experience in teaching/mentoring  as furnished below:
\vspace{0.5em}
\begin{itemize}
\item as a Teaching Assistant during my Master's degree in Indian Institute of Technology Madras,
\item as a Mentor for the project "Going Online As Leader (GOAL)" programme launched by Facebook in partnership with the Ministry of Tribal Affairs (MoTA) GOI (2020 - 2021),
\item as private tutor for Mathematics and Computer Science related subjects.
\end{itemize}

%conclusion
\vspace{1em}
I am sure that my proven ability to manage and maintain the highest decorum as Lecturer will be of utmost beneficial for the institution, and I too believe I can make a significant contribution to the institution as well as to the nation. \\

\vspace{1em}
I look forward to an opportunity to serve as a Guest Lecturer in the Dept. of Computer Application, under "University Name" and be considered for the above-said post.

\vspace{0.5cm}


\makeletterclosing

\end{document}