%------------------------
% John Jones Resume 2022
% Author : John Jones
% Adapted from template https://www.overleaf.com/latex/templates/resume-template-by-anubhav/dhmkrwtksdgy
% License : MIT
%------------------------

\documentclass[a4paper,20pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.530in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.45in}
\addtolength{\textheight}{1in}

\urlstyle{rm}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemWithoutTitle}[1]{
  \item\small{
    {\vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{#3} & \textit{#4} \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-3pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
\newcommand{\urlNewWindow}[1]{\href[pdfnewwindow=true]{https://#1}{\nolinkurl{#1}}}

%-----------------------------
%%%%%%  CV STARTS HERE  %%%%%%

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\LARGE John Jones}} & Email: \href{mailto:johnj.gw@gmail.com}{johnj.gw@gmail.com} \\
  \urlNewWindow{www.linkedin.com/in/john-mt-jones} & Mobile:~+1-785-201-1063
\end{tabular*}

%-----------EDUCATION-----------------
\section{~~Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Kansas State University}{Manhattan, KS}
      {Bachelor of Science - Computer Engineering;  GPA: 3.65}{August 2011 - May 2016}
      {\scriptsize \textit{ \footnotesize{\newline{}Focus on Embedded Systems, Minor in Computer Science
	\newline{}\textbf{Courses:} Data Structures, Computer Design and Operations, Microcontrollers, Electronics, Operating Systems}}}
    \resumeSubHeadingListEnd
	    
\vspace{-10pt}
\section{Skills Summary}
	\resumeSubHeadingListStart
	\resumeSubItem{Languages}{~~~~~~C\#, C, C++, Typescript, Javascript, SQL, Python, PHP, Java, VHDL, Verilog, asm}
	\resumeSubItem{Frameworks}{~~~~.NET, Entity Framework, Angular, Nebular, NodeJS, SignalR, Socket.IO}
	\resumeSubItem{Tools}{~~~~~~~~~~~~~~GIT, PostgreSQL, MySQL, Codacy, MongoDB, Postman, Quartus}
	\resumeSubItem{Platforms}{~~~~~~~Windows, iOS, Linux, Arduino, Raspberry, Microsoft Azure}

\resumeSubHeadingListEnd
\vspace{-5pt}

%-----------EMPLOYMENT-----------------
\section{Employment}
  \resumeSubHeadingListStart
    \resumeSubheading{Rack Performance}{Overland Park, KS}
    {Software Engineer}{Jul 2018 - Apr 2022}
    \resumeItemListStart
        \resumeItem{Back End Development}
          {Developed server side API endpoints in C\# .NET using Entity Framework for SQL data management for weight room management and fitness applications.}
        \resumeItem{Front End Development}
          {Developed front-end UX using Angular, Typescript, Angular Material, and Nebular frameworks. 
            Built real-time web interfaces using Websockets to keep multiple clients in sync.}
        \resumeItem{Testing and Feedback}
          {Iterate on the application based on QA and customer feedback to eliminate bugs and improve user experience.
            Promoted product at various high school clinics and interacted directly with customers.}
        \resumeItem{Deployment}{Deployed to Azure staging environment for pre-deployment smoke tests and production deployment.}
    \resumeItemListEnd

    \resumeSubheading
		{Garmin International}{Olathe, KS}
		{Software Engineer}{July 2016 - May 2018}
		\resumeItemListStart
        \resumeItem{Embedded Software Development}
          {Developed mid to low level software in C for handheld and wearable consumer devices
            including GPSMAP (handheld) 66 \& 276cx, Foretrex 601/701, Fenix 5/5X/5S and others.}
        \resumeItem{Maintenance}
          {Fixed bugs, improved, and deployed software updates for released Garmin products.}
		\resumeItemListEnd

    \resumeSubheading
		{GE Aviation}{Manhattan, KS}
		{Co-op Software Engineer}{Jan 2014 - Jan 2016}
		\resumeItemListStart
        \resumeItem{Employee Metrics Tool}
          {Developed a web-based tool used to track and visualize employee metrics.}
        \resumeItem{Automation Tool}
          {Developed a web-based tool to automate batching of test procedures for aviation software.}
        \resumeItem{Verification Engineer}
          {Worked briefly as a verification engineer writing test procedures for aviation software.}
		\resumeItemListEnd

    \resumeSubheading
		{Kansas State University, Knowledge Discovery \& Data Mining}{Manhattan, KS}
		{Undergraduate Research Assistant Programmer}{2013-2014}
		\resumeItemListStart
        \resumeItem{Paystubs Project}
          {Developed Java program to retrieve and analyze information from paystubs using Optical Character Recognition and basic Natural Language Processing.}
        \resumeItem{Web Crawler}
          {Contributed to a web crawler project designed be lighter weight than any other available crawler at the time.
            I wrote the logic to parse and honor robots.txt files.}
        \resumeItem{Graphical Visualizations}
          {Created graphical JavaScript graphs and charts using the d3.js library.}
		\resumeItemListEnd

    %\resumeSubheading
		%{Ace Hardware Home Center}{Salina, KS}
		%{Customer Service, Cashier}{2008-2011}
		%\resumeItemListStart
    %    \resumeItem{Customer Service}
    %      {Resolved customer complaints and handled returns.}
    %    \resumeItem{Inventory}
    %      {Maintained electronic inventory levels.}
    %    \resumeItem{Online Retail}
    %      {Worked with an online retail partner business, creating and maintaining online retail sales listings, as well as packing and shipping orders.}
		%\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\vspace{-5pt}
\section{Projects}
\resumeSubHeadingListStart
\resumeSubItem{Supersonic Mario}{(Work in progress) Building a mod for Rocket League that allows the player to play as Mario from Super Mario 64 instead of a car.
  Written in C++ using libsm64 (based on a decompilation of the original Super Mario 64 ROM) and custom DirectX11 code for rendering the Mario 64 model.}
\vspace{2pt}
\resumeSubItem{\urlNewWindow{Romhacking.com}}{Built a website to host and aggregate ROM hacks of Super Mario 64. Users can post new hacks, share their progress on 
hacks they have played or are playing, and discuss ideas and issues in the forums section.}
\vspace{2pt}
\resumeSubItem{Piano LED System}{Built a circuit, firmware, web interface using a strip of WS2912B LEDs and a Wi-Fi enabled Mircrocontroller to take MIDI input
  from a digital piano and light LEDs so each key would light a different one.}
  \vspace{2pt}
\resumeSubItem{Codenames Website}{Built a website in NodeJS and Socket.IO to play the popular board game Codenames with friends.}
\vspace{2pt}
\resumeSubItem{N64 to Gamecube Controller Adapter}{Built a custom controller adapter using a microctontroller to convert N64 controller inputs to
  Gamecube. Allowed remapping of controls for games that didn't support it natively. The design used Finite State Machines, and I used an oscilloscope
  to troubleshoot issues.}
\vspace{2pt}
\resumeSubItem{TAS Bot}{Built a bot to play Nintendo 64 Tool Assisted Speedruns (TAS) on the original hardware. This used a Raspberry pi to read the inputs
  on a file system and feed them into a microcontroller to communicate through the Nintendo's controller port at a 1\(\mu\)s resolution. Implemented Finite State
  Machines to handle reading and writing the Nintendo 64's serial controller protocol. Used an oscilloscope to to troubleshoot issues.}
\resumeSubHeadingListEnd

\end{document}